---
title: "Solution Ex4 Duchossois"
author: "Clara Duchossois"
date: "2024-03-20"
output: html-document
---

### Loading libraries

```{r}
library(tidyverse)
library(tidyr)
library(broom)
library(ggplot2)
library(car)
```

### Question 1: Build the linear regression model Yi = b0 + b1ti + εi and estimate b0 and b1.

```{r}
# Create a tibble (dataframe) containing the data collected:
data <- tibble(
  bpm = c(200, 195, 200, 190, 188, 180, 185, 180, 163, 170),
  age = c(10, 20, 21, 25, 29, 30, 31, 40, 45, 50))

# Building the linear regression model
model <- lm(bpm ~ age, data = data)
cat("Model: linear regression model Yi = b0 + b1ti + εi\n")

# Estimate coefficients b0 and b1
b0 <- coef(model)[1]
b1 <- coef(model)[2]

# Printing estimated coefficients
cat("Estimated coefficients:\n")
cat("b0:", b0, "\n")
cat("b1:", b1, "\n")

```

```{r}
# Summary of our linear model and predicted coefficients
summary(model)
```

### Question 2: Verify the null hypothesis H0 : b1 = 0 against the alternative H1 : b1 ≠ 0 with a significance level α = 0.05.

### For this question, we offer two alternative solutions: one using a built-in hypothesis testing function in R, the other using the coefficients given earlier by the summary of the model.

```{r}
# Perform linear hypothesis test on our model. H0 : b1 = 0 (in our case i.e. age = 0)
hypothesis <- linearHypothesis(model, "age = 0")

# Print the results of the linear hypothesis test
hypothesis
```

## Since the p-value (given by Pr(\>F)) of the test (0.0001011) is less than the value of alpha=0.05, we reject the null hypothesis.


```{r}
# Test the hypothesis. We first look at the p-value given by the model summary for the coefficient b1
p_value <- summary(model)$coefficients[2, "Pr(>|t|)"]

cat("Hypothesis testing:\n\n")
cat("p-value:", p_value, "\n\n")

alpha <- 0.05
if (p_value < alpha) {
  cat("We reject the null hypothesis.\nWe conclude that there is a significant relationship between beats per minute under stress and age.\n")
} else {
  cat("We accept the null hypothesis.\nWe conclude that there is no significant relationship between beats per minute under stress and age.\n")
}
```
